---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis
```{r}
setwd("~/Desktop/Experimental methods 3/Assignment 5")

data <- read.csv("~/Desktop/Experimental methods 3/Assignment 5/Data.csv", sep=";")

library(readr)
library(dplyr)
library(metafor)
library(lmerTest)
library(lme4)
```

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 
```{r}
PitchRange=escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = data)

model_mean <- lmer(yi ~ 1 + (1 | Article), weights = 1/vi, data=PitchRange, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_mean)

res_mean <- rma(yi, vi, data = PitchRange, slab=Article)
summary(res_mean)
forest(res_mean)


PitchRangeSD=escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = data)


model_sd <- lmer(yi ~ 1 + (1 | Article), weights = 1/vi, data=PitchRange, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(model_sd)

res_sd <- rma(yi, vi, data = PitchRangeSD, slab=Article)
summary(res_sd)
forest(res_sd)
```

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.
```{r}
#data from assignment 3 part 2
A3 <- read_csv("~/Desktop/Experimental methods 3/A3-P2/final_rqa.csv")

#creating new dataframes. A3 controls and A3 schizo
controls = A3[A3$diagnosis =="control", ]
schizo = A3[A3$diagnosis =="schizophrenia", ]

PitchMeanControls = mean(controls$mean)
PitchMeanSchizo = mean(schizo$mean)

PitchSDControls = mean(controls$stdDev)
PitchSDSchizo = mean(schizo$stdDev)

SampleSizeContros = length(unique(controls$participant))
SampleSizeSchizo =  length(unique(schizo$participant))
  
PitchMeanControlsSD = sd(controls$mean) 
PitchMeanSchizoSD = sd(schizo$mean)

PitchSDControlsSD = sd(controls$stdDev) 
PitchSDSchizoSD = sd(schizo$stdDev)

Article = "Assignment 3"

Year = "2017"


df_A3 = data.frame(Article, Year, SampleSizeSchizo ,SampleSizeContros, PitchMeanControls, PitchMeanControlsSD, PitchMeanSchizo,PitchMeanSchizoSD, PitchSDControls, PitchSDControlsSD, PitchSDSchizo, PitchSDSchizoSD)

data2 = rbind(data,df_A3)

#If you add your results to the meta-analysis, do the estimated effect sizes change?
PitchRange2=escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = data2)

res_mean2 <- rma(yi, vi, data = PitchRange2, slab=Article)
summary(res_mean2)
forest(res_mean2)


PitchRangeSD2=escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeContros, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = data2)

res_sd2 <- rma(yi, vi, data = PitchRangeSD2, slab=Article)
summary(res_sd2)
forest(res_sd2)
```
3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.
```{r}
#funnel plot on meta-analysis with assignment 3 - sd
fplot_sd=funnel(res_sd2, main = "Random-Effects Model", xlab = "Standardized Mean Difference") 
inf_sd <- influence(res_sd2) 
print(inf_sd) 
plot(inf_sd)
ranktest(res_sd2)


#funnel plot on meta-analysis with assignment 3 - mean
fplot_mean=funnel(res_mean2, main = "Random-Effects Model", xlab = "Standardized Mean Difference") 
inf_mean <- influence(res_mean2) 
print(inf_mean) 
plot(inf_mean)
ranktest(res_mean2)

```
## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2
